---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bis620.2023

<!-- badges: start -->
[![R-CMD-check](https://github.com/XunyunWan/bis620.2023/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/XunyunWan/bis620.2023/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/XunyunWan/bis620.2023/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/XunyunWan/bis620.2023/actions/workflows/test-coverage.yaml)
<!-- badges: end -->


The goal of bis620.2023 is to provide a comprehensive and user-friendly platform for exploring and visualizing clinical trial data. Our app emphasizes key aspects, including age, participation timeline, collaborative leadership, and the nature of experiments. Users can easily filter and analyze clinical trials based on these criteria, gaining insights into the safety, effectiveness, and overall progress of treatments. Additionally, the app offers spatial visualizations of participating countries and an overview of trial statuses. This tool aims to facilitate data-driven decision-making in healthcare research. Explore the diverse world of clinical trials with bis620.2023 for enhanced medical science and improved healthcare outcomes.

## Installation

You can install the development version of bis620.2023 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("XunyunWan/bis620.2023")
```
## Feature  

### Age range  
This feature displays and categorizes the age of participants. By adjusting the age
range, users of this app can view experiments for the target age range. It provides
insights into the safety and effectiveness of treatments across age groups.  

### Date range  
This feature captures the trial start and end dates. Users of this app can filter studies for the time period of interest by adjusting the date range to help track trends and ongoing trial progress.  

### Collaborators or leaders  
This feature is used to classify and identify leadership or cooperative trials. Users of this app can view the people behind the experiment by selecting different categories, helping to assess expertise and potential bias. In clinical trials, each NCT ID (National Clinical Trial Identifier) represents a specific clinical trial project. Each NCT ID can contain multiple studies, and the order in which these studies are arranged can vary, but in most studies, it is arranged in chronological order based on their start date or planned date, from the earliest study to the most recent. In this app, we selected the first study in each clinical trial identifier and display its data of collaborator or leader. We believe the earliest stage of the trial is the best phase to represent how the whole study is shaped and is of the most value for users’ reference.  

### Type of Study  
This feature classifies trials into types such as Interventional (clinical trial) or
observational studies. Users of this app can view experiments of different natures by
selecting different categories, which can give users a clearer and more accurate
reference for similar experiments and provide a background for understanding
experimental methods.  

### Spatial visualization of participating countries  
This function spatially visualizes the countries of clinical trials and performs
geographical stratification and coloring according to the number of trials conducted. Users of this app can very intuitively observe the geographical scale of clinical trial participation, which helps to understand the global distribution of clinical trials. . Provide a reference for subsequent research on geographical analysis and spatio-temporal distribution statistics.  

### Overall status distribution visualization  
This feature provides a clear view of trial progress and results, so clinical trials show the distribution of trials by trial status (e.g., ongoing, completed). Through such visualization, users of this app can grasp the general status of the entire clinical trial and estimate the progress of the trial.


## Example

This is a basic example which we use in shinyApp to demonstrate different phases:

```{r, example, message=FALSE,warning =FALSE,echo = FALSE}
library(bis620.2023)

bis620.2023:::plot_phase_histogram(studies)

```

